Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-23 paper/main.tex
correct typo
rephrase table caption of annotated events

\noindent Generally
\begin{itemize]}
    \item Todo's are mostly comments and can be deleted if issue is solved by
        current phrasing
    \item position of figures and tables is very odd now but probably does not
        matter
\end{itemize}

@@

    Some of the noun categories (female, females, fname; male,
    males, mname; face, head; object, objects;
    Tab.~\ref{tab:descr-nouns-rules}) were pooled
    into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead},
    \texttt{object}).

@@

% we checked correlations
Given the unknown confound structure of the naturalistic stimuli, we inspected
% correlations within stimuli and across stimuli
the correlation of regressors across the eight segments of each stimulus and
also across both stimuli (Fig.~\ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli
Maximum correlations are found for auditory low-level confounds across stimuli
(\texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
\texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77),
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (Fig. \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
The observed correlation pattern did not indicate problematic confounds of
nuisance variables and regressors of interest for any of the planned
analyses.

>>>>

\noindent Generally
\begin{itemize}
    \item Todo's are mostly comments and can be deleted if issue is solved by
        current phrasing
    \item position of figures and tables is very odd now but probably does not
        matter
\end{itemize}

@@

    Some of the audio-description's event categories listed here
    (\texttt{sex\_f}; \texttt{sex\_m}; \texttt{fahead}, \texttt{object})
    were created by pooling some categories of the original annotation of nouns
    (female, females, fname; male, males, mname; face, head; object, objects;
    Tab.~\ref{tab:descr-nouns-rules}).

@@

\todo[inline]{SE: "the eight segments": Are you sure, everybody remembered
these? COH: no clue what to do with that feedback}
% we checked correlations
Given the unknown confound structure of the naturalistic stimuli, we inspected
% correlations within stimuli and across stimuli
the correlation of regressors across the eight segments of each stimulus and
also across both stimuli (Fig.~\ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli
Maximum correlations are found for auditory low-level confounds across stimuli
(\texttt{fg\_a(v|d)\_ger\_rms}, r=.76; \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77),
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (Fig. \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
The observed correlation pattern did not indicate problematic confounds of
nuisance variables and regressors of interest for any of the planned analyses.
